---
title: "Relationship Between Age and Feelings of Life, 2017"
author: "Juan Acosta"
date: "October 19, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(brms)
library(tidyverse)

gss <- read_csv("gss.csv")
```

## Title of your Report
Relationship Between Age and Feelings of Life, 2017

# Name(s) of Author(s) 
Juan Acosta

# Date
October 19, 2020

## Abstract

In this paper, I will examine the correlation between age and feelings of life (rated on a scale from 1 to 10) in Canada during the year 2017, using a linear regression model represented through a plot.

## Introduction

The goal of this analysis is to see whether there is a relation between how Canadians feel about their lives in general and their age. Feelings about life can be attributed to satisfaction with education, wealth, relationships, and a plethora of other factors. This analysis aims to see whether Canadians are more optimistic as they age, more pessimistic, a mix of both, or if there is even a relationship between age and life satisfaction.

## Data

The data I am using is the GSS data from 2017, using the *age* variable and the *feelings_life* variable.

## Model

I am using a linear regression model represented through a plot. 

## Results

### Figure 1
```{r, echo=FALSE}
gss %>% 
  ggplot(aes(x = age, y = feelings_life)) +
  geom_point()
```

# Discussion

As can be seen in Figure 1, there is no definitive correlation between age and feelings of life. A line of best fit drawn through the plot would approach a vertical slope, meaning there can be no conclusion about the relationship between the independent (age) and dependent (feelings_life) variables.

However, an interesting point to note is that for the lower ratings attributed to feelings of life, they tend to skew more towards the older population. That is, less young people feel pessimistic about life, while an equal spread of the population feel more optimistic.

What this signifies in terms of the analysis is the following: Feelings on life do not depend on ones age. A young person can be as satisfied about their life as an older person, and the same can be said of dissatisfaction with ones life.

# Weaknesses

A clear weakness of the data is that it is not always conducive to studying it using linear regression methods, as can be seen with the indecisiveness of the plot presented in Figure 1. Another weakness is that there is a sizable portion of data missing, so I am not working with a complete data set. This can have a negative impact on the reliability of the results established in this analysis.

# Next Steps

A possible next step can include analyzing data from other years to see if the same conclusion from 2017 is present in those other years.

# GitHub Repo Link

Link to the GitHub repo: https://github.com/SimiDavid95/Problem-Set-2

## References
Alexander, R., & Caetano, S. (2020, October 7). [Gss_cleaning.R].